03-modeling

### 2018-07-11 02_scripts/01_hyperspectral_indices/08_extract_bands_to_points.Rmd
11/07/2018

```{r, results='hide'}
library(raster)
devtools::install_github("pat-s/hsdar")
library(hsdar)
library(pbmcapply)
library(glue)
library(magrittr)
library(sf)
library(purrr)
library(dplyr)
```

@@

  ras_veg_indices <- brick(glue("/data/patrick/mod/hyperspectral/all-veg-indices/{plot_name}.grd"))

  ras_nbi <- brick(glue("/data/patrick/mod/hyperspectral/narrow-band-indices/narrow-band-indices-{plot_name}.grd"))

  # calculate buffered veg index
  out_veg <- pbmclapply(buffer, function(x) 
    raster::extract(ras_veg_indices, points, buffer = x, 
                    fun = mean, df = TRUE,
                    na.rm = TRUE), mc.cores = cores)

  out_veg %<>% 
    map2(seq_along(buffer), ~ setNames(.x, glue("bf{buffer}_{name}", 
                                             name = names(out_veg[[.y]]))))

  out_nbi <- pbmclapply(buffer, function(x)
    raster::extract(ras_nbi, points, buffer = x,
                    fun = mean, df = TRUE,
                    na.rm = TRUE) , mc.cores = cores)

  out_nbi %<>%
    map2(seq_along(buffer), ~ setNames(.x, glue("bf{buffer}_{name}",
                                             name = names(out_nbi[[.y]]))))

  # merge all data frames (buffers)
  all_veg <- bind_cols(out_veg)

  all_nbi <- bind_cols(out_nbi)

  points %<>% 
    bind_cols(all_veg) %>% 
    bind_cols(all_nbi)

  # .rda file (data frame)
  points %>% 
    saveRDS(glue("/data/patrick/mod/tree-per-tree/2016/{plot_name}/all-indices-{plot_name}_{bf_name}.rda"))
}
```

@@

```{r}
pbmclapply(c("laukiz1", "laukiz2", "oiartzun", "luiando"), 
           function(x) extract_to_plot(x, 2, cores = 1, "bf2"), 
           mc.cores = 4)
```

>>>>

```{r, results='hide'}
library(raster)
devtools::install_github("pat-s/hsdar")
library(hsdar)
library(pbmcapply)
library(glue)
library(magrittr)
library(sf)
library(purrr)
library(dplyr)
library(furrr)
```

@@

  bands_ras <- brick(glue("/data/patrick/mod/hyperspectral/atm-cropped/{plot_name}.tif"))

  # calculate buffered veg index

  # plan(multiprocess)
  # out_bands <- future_map(buffer, ~
  #   raster::extract(bands_ras[[5:126]], points, buffer = .x, 
  #                   fun = mean, df = TRUE,
  #                   na.rm = TRUE),.progress = TRUE)

  out_bands <- pbmclapply(buffer, function(x)
    raster::extract(bands_ras[[5:126]], points, buffer = x,
                    fun = mean, df = TRUE,
                    na.rm = TRUE), mc.cores = cores)

  out_bands %<>% 
    map2(seq_along(buffer), ~ setNames(.x, glue("bf{buffer}_{name}", 
                                             name = names(out_bands[[.y]]))))

  # merge all data frames (buffers)
  out_bands <- bind_cols(out_bands)

  points %<>% 
    bind_cols(out_bands)

  # .rda file (data frame)
  points %>% 
    saveRDS(glue("/data/patrick/mod/tree-per-tree/2016/{plot_name}/all-bands-{plot_name}_{bf_name}.rda"))
}
```

@@

```{r}
# plan(multiprocess)
# future_map(c("laukiz1", "laukiz2", "oiartzun", "luiando"), ~
#            extract_to_plot(.x, 2, "bf2"), .progress = TRUE)
pbmclapply(c("laukiz1", "laukiz2", "oiartzun", "luiando"), 
           function(x) extract_to_plot(x, 2, cores = 1, "bf2"), 
           mc.cores = 4)
```

### 2018-07-11 02_scripts/022_preprocessing.Rmd
11/07/2018

```{r}
data %<>% 
  map(~ dplyr::select(.x, -contains("_ID"))) %>% 
  map(~ as.data.table(.x)) %>% 
  map(~ Filter(function(x) !any(is.na(x)), .x))
```

>>>>

luiando has some NA obs that need to be removed, otherwise the whole column will be removed by `Filter()`

```{r}
data[[3]] %<>% 
  na.omit()

data %<>% 
  map(~ dplyr::select(.x, -contains("_ID"))) %>% 
  map(~ as.data.table(.x)) %>% 
  #map(~ na.omit(.x)) %>% # some obs in luiando are NA after extraction
  map(~ dplyr::select(.x, -tree.number, -decoloration, -canker, -diameter, -height)) %>% 
  map(~ Filter(function(x) !any(is.na(x)), .x))
```

### 2018-07-11 02_scripts/031-laukiz1/03-modeling_laukiz1.Rmd
11/07/2018

```{r, results='hide'}
library(mlr)
library(glue)
library(sf)
library(dplyr)
library(tibble)
library(purrr)
library(magrittr)
library(data.table)
library(pbmcapply)
```

@@

```{r}
task = makeRegrTask(id = "laukiz1", data = data, 
                    target = "deftot", coordinates = coords)
```

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 102, upper = 10228))
```

```{r}
ctrl <- makeTuneControlRandom(maxit = 200)
inner <- makeResampleDesc("SpCV", iters = 10)
```

@@

```{r}
tune_wrapper <- makeTuneWrapper(lrn_glmnet, resampling = inner, par.set = ps_glmnet,
                                control = ctrl, show.info = TRUE,
                                measures = list(rmse))
```

@@

```{r}
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.tuneParams", cpus = 40,
              mc.set.seed = TRUE) # only parallelize the tuning

@@

```{r}
configureMlr(on.learner.error = "warn", on.error.dump = TRUE)
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.tuneParams", cpus = 48,
              mc.set.seed = TRUE) # only parallelize the tuning
set.seed(12345)
params_tuned_glmnet = tuneParams(lrn_glmnet, task = task, resampling = inner,
                                 par.set = ps_glmnet, control = ctrl, 
                                 measure = list(rmse))
parallelStop()
saveRDS(params_tuned_glmnet, "/data/patrick/mod/tmp/tuning_hyperspectral/tuning_bf2_ridge.rda")
```

@@

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 0.1, upper = 10.3))
```

```{r}
ctrl <- makeTuneControlRandom(maxit = 200)
inner <- makeResampleDesc("SpCV", iters = 10)
```

@@

```{r}
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.tuneParams", cpus = 48,
              mc.set.seed = TRUE) # only parallelize the tuning

@@

parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/laukiz1_lasso_bf2_10folds.rda")
resa_glmnet = readRDS("/data/patrick/mod/hyperspectral/spcv/laukiz1_lasso_bf2_10folds.rda")
```

@@

```{r}
configureMlr(on.learner.error = "warn", on.error.dump = TRUE)
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.tuneParams", cpus = 40,
              mc.set.seed = TRUE) # only parallelize the tuning
set.seed(12345)
params_tuned_glmnet = tuneParams(lrn_glmnet, task = task, resampling = inner,
                                 par.set = ps_glmnet, control = ctrl, 
                                 measure = list(rmse))
parallelStop()
```

@@

@@

```{r}
tibble(index = rownames(as.matrix(coef(glmnet_train_tuned$learner.model, s = 1810))), 
       coef = as.vector(as.matrix(coef(glmnet_train_tuned$learner.model, s = 1810)))) %>% 
  arrange(desc(coef))
```
```{r}
tibble(index = rownames(as.matrix(coef(glmnet_train_tuned$learner.model, s = 1810))), 
       coef = as.vector(as.matrix(coef(glmnet_train_tuned$learner.model, s = 1810)))) %>% 
  arrange(coef)
```

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 0.1, upper = 10228),
                          makeNumericParam("alpha", lower = 0, upper = 1))
```

```{r}
ctrl <- makeTuneControlRandom(maxit = 200)
inner <- makeResampleDesc("SpCV", iters = 10)
```

@@

```{r}
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.tuneParams", cpus = 40,
              mc.set.seed = TRUE) # only parallelize the tuning

@@

```{r}
configureMlr(on.learner.error = "warn", on.error.dump = TRUE)
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.tuneParams", cpus = 48,
              mc.set.seed = TRUE) # only parallelize the tuning
set.seed(12345)
params_tuned_glmnet = tuneParams(lrn_glmnet, task = task, resampling = inner,
                                 par.set = ps_glmnet, control = ctrl, 
                                 measure = list(rmse))
parallelStop()
```

>>>>

```{r, results='hide'}
library(mlr)
library(mlrMBO)
library(glue)
library(sf)
library(dplyr)
library(tibble)
library(purrr)
library(magrittr)
library(data.table)
library(pbmcapply)
library(stringr)
library(ggpubr)
```

@@

```{r}
task = makeRegrTask(id = "laukiz1", data = data, 
                    target = "defoliation", coordinates = coords)
```

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 78, upper = 7879))
```

```{r}
ctrl = makeMBOControl(propose.points = 1L)
ctrl = setMBOControlTermination(ctrl, iters = 70L)
ctrl = setMBOControlInfill(ctrl, crit = crit.ei)
ctrl = setMBOControlMultiPoint(ctrl, method = "cl", cl.lie = min)
tune.ctrl = makeTuneControlMBO(mbo.control = ctrl,
                               mbo.design = generateDesign(n = 30, par.set =  ps_glmnet))
inner <- makeResampleDesc("SpCV", iters = 10)
```

@@

```{r}
tune_wrapper <- makeTuneWrapper(lrn_glmnet, resampling = inner, par.set = ps_glmnet,
                                control = tune.ctrl, show.info = TRUE,
                                measures = list(rmse))
```

@@

```{r}
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.resample", cpus = 20,
              mc.set.seed = TRUE) # only parallelize the tuning

@@

```{r}
configureMlr(on.learner.error = "warn", on.error.dump = TRUE)
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.tuneParams", cpus = 48,
              mc.set.seed = TRUE) # only parallelize the tuning
set.seed(12345)
params_tuned_glmnet = tuneParams(lrn_glmnet, task = task, resampling = inner,
                                 par.set = ps_glmnet, control = tune.ctrl, 
                                 measure = list(rmse))
parallelStop()
saveRDS(params_tuned_glmnet, "/data/patrick/mod/tmp/tuning_hyperspectral/tuning_bf2_ridge.rda")
```

@@

#### Important spectral regions

Get the first 100 most important indices.
We take the absolute value of the coefficient to consider both sides.

We only take the top 100 indices so that the result is not cluttered by mid-ranged indices summping up in the end-result.
Apparently, we have 56 unique bands within the top 100 indices.

```{r}
tibble(index = rownames(as.matrix(coef(glmnet_train_tuned$learner.model, s = 7500))), 
       coef = abs(as.vector(as.matrix(coef(glmnet_train_tuned$learner.model, s = 7500))))) %>% 
  arrange(desc(coef)) %>% 
  mutate(coef = coef) -> top_inds_rr_laukiz1
saveRDS(top_inds_rr_laukiz1, "/data/patrick/mod/hyperspectral/top-inds/top_inds_rr_laukiz1.rda")
```

Remove the "bf2" information and filter out NRI only.

```{r}
top_inds_rr_laukiz1 %<>% 
  mutate(index = str_sub(index, 9, 15)) %>% 
  filter(str_detect(index, "b"))
```

Standardize the coefficients

```{r}
top_inds_rr_laukiz1 %<>% 
  mutate(coef = as.numeric((coef / min(coef)) * coef))
```

Extract all band numbers.

```{r}
top_inds_rr_laukiz1 %>% 
  dplyr::select(index) %>% 
  str_match_all("[0-9]+") %>% 
  flatten() %>% 
  as.numeric() -> all_bands_rr
```

```{r}
hist(all_bands_rr)
```

Now add a weight to all bands.
Starting from 100-2 depending on the score.
why 2? Because we only have 198 values because we removed one vegetation index.

```{r}
tibble(band = all_bands_rr, weight = rep(top_inds_rr_laukiz1$coef, times = 1, each = 2)) %>% 
  group_by(band) %>% 
  summarise(score = sum(weight)) %>% 
  mutate(band = band) %>% 
  arrange(desc(score)) -> tibble_most_imp
```

Classify the bands into spectral regions

1 - 60: visible (404 - 680)
61 - 71: red edge (680 - 730)
72 - 126: NIR (730 - 996)

```{r}
tibble_most_imp %<>% 
  mutate(group = as.factor(case_when(band <= 60 ~ "Visible (404 - 680)", 
                           (band >= 61 & band <= 71) ~ "Red Edge (680 - 730)",
                           band >= 72 ~ "NIR (730 - 996)"))) %>% 
  arrange(desc(score)) %>% 
  mutate(band = as.factor(band))
```

centered by the mean of the scaled coefficients.

```{r}
ggdotchart(tibble_most_imp, x = "band", y = "score",                              # Color by groups
           sorting = "descending",                       # Sort value in descending order
           add = "segments",                             # Add segments from y = 0 to dots
           color = "group",
           palette = "nejm",
           group = "score",
           combine = T,
           rotate = TRUE,                                # Rotate vertically
           dot.size = 1,                                 # Large dot size
           #label = round(tibble_most_imp$sum),                        # Add mpg values as dot labels
           ggtheme = theme_pubr(base_size = 9, margin = FALSE)) + 
  labs(y = "Score", color = "Spectral regions")
```

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 0.07, upper = 7.87))
```

```{r}
ctrl = makeMBOControl(propose.points = 1L)
ctrl = setMBOControlTermination(ctrl, iters = 70L)
ctrl = setMBOControlInfill(ctrl, crit = crit.ei)
ctrl = setMBOControlMultiPoint(ctrl, method = "cl", cl.lie = min)
tune.ctrl = makeTuneControlMBO(mbo.control = ctrl,
                               mbo.design = generateDesign(n = 30, par.set =  ps_glmnet))
inner <- makeResampleDesc("SpCV", iters = 10)
```

@@

```{r}
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.resample", cpus = 10,
              mc.set.seed = TRUE) # only parallelize the tuning

@@

parallelStop()
saveRDS(resa_glmnet, "/data/patrick/mod/hyperspectral/spcv/laukiz1_lasso_bf2_10folds.rda")
```

@@

```{r}
configureMlr(on.learner.error = "warn", on.error.dump = TRUE)
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.tuneParams", cpus = 40,
              mc.set.seed = TRUE) # only parallelize the tuning
set.seed(12345)
params_tuned_glmnet = tuneParams(lrn_glmnet, task = task, resampling = inner,
                                 par.set = ps_glmnet, control = tune.ctrl, 
                                 measure = list(rmse))
parallelStop()
```

@@

```{r}
lrn_glmnet_tuned <- makeLearner("regr.glmnet",
                                alpha = 1,
                                s = 1810,
                                standardize = FALSE, 
                                intercept = FALSE)
#lambda = sort(seq(0, 5, length.out = 100), decreasing = T))
glmnet_train_tuned = mlr::train(lrn_glmnet_tuned, task)
```

@@

```{r}
tibble(index = rownames(as.matrix(coef(glmnet_train_tuned$learner.model, s = 1810))), 
       coef = as.vector(as.matrix(coef(glmnet_train_tuned$learner.model, s = 1810)))) %>% 
  arrange(desc(coef))
```

```{r}
tibble(index = rownames(as.matrix(coef(glmnet_train_tuned$learner.model, s = 1810))), 
       coef = as.vector(as.matrix(coef(glmnet_train_tuned$learner.model, s = 1810)))) %>% 
  arrange(coef)
```

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 0.07, upper = 7879),
                          makeNumericParam("alpha", lower = 0, upper = 1))
```

```{r}
ctrl = makeMBOControl(propose.points = 1L)
ctrl = setMBOControlTermination(ctrl, iters = 70L)
ctrl = setMBOControlInfill(ctrl, crit = crit.ei)
ctrl = setMBOControlMultiPoint(ctrl, method = "cl", cl.lie = min)
tune.ctrl = makeTuneControlMBO(mbo.control = ctrl,
                               mbo.design = generateDesign(n = 30, par.set =  ps_glmnet))
inner <- makeResampleDesc("SpCV", iters = 10)
```

@@

```{r}
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.resample", cpus = 10,
              mc.set.seed = TRUE) # only parallelize the tuning

@@

```{r}
configureMlr(on.learner.error = "warn", on.error.dump = TRUE)
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.tuneParams", cpus = 48,
              mc.set.seed = TRUE) # only parallelize the tuning
set.seed(12345)
params_tuned_glmnet = tuneParams(lrn_glmnet, task = task, resampling = inner,
                                 par.set = ps_glmnet, control = tune.ctrl, 
                                 measure = list(rmse))
parallelStop()
```

### 2018-07-11 02_scripts/032-laukiz2/03-modeling_laukiz2.Rmd
11/07/2018

```{r, results='hide'}
library(mlr)
library(glue)
library(sf)
library(dplyr)
library(tibble)
library(purrr)
library(magrittr)
library(data.table)
library(pbmcapply)
```

@@

```{r}
task = makeRegrTask(id = "laukiz2", data = data, 
                    target = "deftot", coordinates = coords)
```

@@

```{r}
ctrl <- makeTuneControlRandom(maxit = 200)
inner <- makeResampleDesc("SpCV", iters = 10)
```

@@

```{r}
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.tuneParams", cpus = 40,
              mc.set.seed = TRUE) # only parallelize the tuning

@@

```{r}
configureMlr(on.learner.error = "warn", on.error.dump = TRUE)
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.tuneParams", cpus = 48,
              mc.set.seed = TRUE) # only parallelize the tuning
set.seed(12345)
params_tuned_glmnet = tuneParams(lrn_glmnet, task = task, resampling = inner,
                                 par.set = ps_glmnet, control = ctrl, 
                                 show.info = TRUE, measure = list(rmse))
parallelStop()
saveRDS(params_tuned_glmnet, "/data/patrick/mod/tmp/tuning_hyperspectral/tuning_bf2_ridge.rda")
```

@@

@@

```{r}
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.tuneParams", cpus = 48,
              mc.set.seed = TRUE) # only parallelize the tuning

@@

>>>>

```{r, results='hide'}
library(mlr)
library(mlrMBO)
library(glue)
library(sf)
library(dplyr)
library(tibble)
library(purrr)
library(magrittr)
library(data.table)
library(pbmcapply)
```

@@

```{r}
task = makeRegrTask(id = "laukiz2", data = data, 
                    target = "defoliation", coordinates = coords)
```

@@

```{r}
ctrl = makeMBOControl(propose.points = 1L)
ctrl = setMBOControlTermination(ctrl, iters = 70L)
ctrl = setMBOControlInfill(ctrl, crit = crit.ei)
ctrl = setMBOControlMultiPoint(ctrl, method = "cl", cl.lie = min)
tune.ctrl = makeTuneControlMBO(mbo.control = ctrl,
                               mbo.design = generateDesign(n = 30, par.set =  ps_glmnet))
inner <- makeResampleDesc("SpCV", iters = 10)
```

@@

```{r}
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.resample", cpus = 40,
              mc.set.seed = TRUE) # only parallelize the tuning

@@

```{r}
configureMlr(on.learner.error = "warn", on.error.dump = TRUE)
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.tuneParams", cpus = 48,
              mc.set.seed = TRUE) # only parallelize the tuning
set.seed(12345)
params_tuned_glmnet = tuneParams(lrn_glmnet, task = task, resampling = inner,
                                 par.set = ps_glmnet, control = tune.ctrl, 
                                 show.info = TRUE, measure = list(rmse))
parallelStop()
saveRDS(params_tuned_glmnet, "/data/patrick/mod/tmp/tuning_hyperspectral/tuning_bf2_ridge.rda")
```

@@

#### Important spectral regions

Get the first 100 most important indices.
We take the absolute value of the coefficient to consider both sides.

We only take the top 100 indices so that the result is not cluttered by mid-ranged indices summping up in the end-result.

```{r}
tibble(index = rownames(as.matrix(coef(glmnet_train_tuned$learner.model, s = 7690))), 
       coef = abs(as.vector(as.matrix(coef(glmnet_train_tuned$learner.model, s = 7690))))) %>% 
  arrange(desc(coef)) %>% 
  mutate(coef = coef) -> top_inds_rr_laukiz2
saveRDS(top_inds_rr_laukiz2, "/data/patrick/mod/hyperspectral/top-inds/top_inds_rr_laukiz2.rda")
```

@@

```{r}
library(parallelMap)
parallelStart(mode = "multicore", level = "mlr.resample", cpus = 20,
              mc.set.seed = TRUE) # only parallelize the tuning

@@

### SVM

```{r}
lrn_ksvm <- makeLearner("regr.ksvm",
                        kernel = "rbfdot")
```

```{r}
ps_svm <- makeParamSet(makeNumericParam("C", lower = -15, upper = 15,
                                        trafo = function(x) 2 ^ x),
                       makeNumericParam("sigma", lower = -15, upper = 15,
                                        trafo = function(x) 2 ^ x))
```

```{r}
ctrl = makeMBOControl(propose.points = 1L)
ctrl = setMBOControlTermination(ctrl, iters = 70L)
ctrl = setMBOControlInfill(ctrl, crit = crit.ei)
ctrl = setMBOControlMultiPoint(ctrl, method = "cl", cl.lie = min)
tune.ctrl = makeTuneControlMBO(mbo.control = ctrl,
                               mbo.design = generateDesign(n = 30, par.set = ps_svm))
inner <- makeResampleDesc("SpCV", iters = 10)
```

```{r}
tune_wrapper <- makeTuneWrapper(lrn_ksvm, resampling = inner, par.set = ps_svm,
                                control = tune.ctrl, show.info = TRUE,
                                measures = list(rmse))
```

```{r}
library(parallelMap)
parallelStart(mode = "multicore", cpus = 40, level = "mlrMBO.feval",
              mc.set.seed = TRUE) # only parallelize the tuning
set.seed(12345)
resa_svm <- mlr::resample(tune_wrapper, task,
                          resampling = outer, extract = getTuneResult,
                          show.info = TRUE, measures = list(rmse))

parallelStop()
saveRDS(resa_svm, "/data/patrick/mod/hyperspectral/spcv/laukiz2_svm.rda")
```

### 2018-07-11 02_scripts/033-luiando/03-modeling_luiando.Rmd
11/07/2018

```{r}
task = makeRegrTask(id = "luiando", data = data, 
                    target = "deftot", coordinates = coords)
```

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 15, upper = 1558))
```

```{r}
ctrl <- makeTuneControlRandom(maxit = 200)
inner <- makeResampleDesc("SpCV", iters = 10)
```

@@

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 0.01, upper = 1.56))
```

```{r}
ctrl <- makeTuneControlRandom(maxit = 200)
inner <- makeResampleDesc("SpCV", iters = 10)
```

>>>>

```{r}
task = makeRegrTask(id = "luiando", data = data, 
                    target = "defoliation", coordinates = coords)
```

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 10, upper = 10000))
```

```{r}
ctrl = makeMBOControl(propose.points = 1L)
ctrl = setMBOControlTermination(ctrl, iters = 70L)
ctrl = setMBOControlInfill(ctrl, crit = crit.ei)
ctrl = setMBOControlMultiPoint(ctrl, method = "cl", cl.lie = min)
tune.ctrl = makeTuneControlMBO(mbo.control = ctrl,
                               mbo.design = generateDesign(n = 30, par.set = ps_glmnet))
inner <- makeResampleDesc("SpCV", iters = 10)
```

@@

#### Important spectral regions

Get the first 100 most important indices.
We take the absolute value of the coefficient to consider both sides.

We only take the top 100 indices so that the result is not cluttered by mid-ranged indices summping up in the end-result.

```{r}
tibble(index = rownames(as.matrix(coef(glmnet_train_tuned$learner.model, s = 1560))), 
       coef = abs(as.vector(as.matrix(coef(glmnet_train_tuned$learner.model, s = 1560))))) %>% 
  arrange(desc(coef)) %>% 
  mutate(coef = coef * 10000000000000000000000000000000000) -> top_inds_rr_luiando
saveRDS(top_inds_rr_luiando, "/data/patrick/mod/hyperspectral/top-inds/top_inds_rr_luiando.rda")
```

@@

```{r}
ps_glmnet <- makeParamSet(makeNumericParam("s", lower = 0.01, upper = 15000))
```

```{r}
ctrl = makeMBOControl(propose.points = 1L)
ctrl = setMBOControlTermination(ctrl, iters = 70L)
ctrl = setMBOControlInfill(ctrl, crit = crit.ei)
ctrl = setMBOControlMultiPoint(ctrl, method = "cl", cl.lie = min)
tune.ctrl = makeTuneControlMBO(mbo.control = ctrl,
                               mbo.design = generateDesign(n = 30, par.set =  ps_glmnet))
inner <- makeResampleDesc("SpCV", iters = 10)
```
